### 2015-02-18 paper_50_sdlc-ae.tex
adding raw tables diagram

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   layout the structure of tables and relationships necessary to the store all the data
   within a relational database such as MySQL or PostgreSQL.  Eventually,
   database diagrams and SQL scripts will be provided in the section.

>>>>

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   lay out the structure of tables and relationships necessary to the store all the data
   within a relational database.

   \subsubsection{TABLES FOR RAW MPI DATA}

        The first set of tables that need to be created are tables
        to store the raw data that is collected.  These tables
        will line up with the necessary data for each of the 5 elements
        of MPI.  Figure \ref{fig:raw} provides a visual description
        of the tables that are needed.  The tables have no relationship
        with each other since they are raw data.  The primary goal of
        these tables is to store the raw data in a single database. The
        5 table names are:
        \begin{enumerate}
            \item QUALITY\_RAW
            \item AVAILABILITY\_RAW
            \item SATISFACTION\_RAW
            \item SCHEDULE\_RAW
            \item REQUIREMENTS\_RAW
        \end{enumerate}
        Notice these table names match with the 5 elements of MPI.

       \begin{figure}[ht]
            \centering
            \includegraphics[scale=.55]{images/raw_tables.png}
            \caption{TABLES FOR RAW MPI DATA}
            \label{fig:raw}
        \end{figure}%

        Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
        database tables for storing the raw MPI data.  The SQL is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

    \subsubsection{INTERMEDIATE SCORE TABLES FOR MPI}

        Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the intermediate MPI scores.

    \subsubsection{FINAL SCORE TABLES FOR MPI}

        Appendix \ref{src:overallscoreSQL} provides the necessary SQL statements to create the 
        database tables for storing the final scores for each element and the final 
        overall MPI scores for each time frequency.
